Manuscript Figures for Genome Biology

### 2018-07-05 manuscript_figures/manuscript_figures.Rmd
Add points to casestudy vs sim ranks boxplots

```{r}
casestudy.tab <- mutate(casestudy.tab, prop_casestudy = mean_prop) %>%
  select(casestudy, method, prop_casestudy)
yeastsim.tab <- yeastsim.tab %>% 
  mutate(prop_yeastsim = mean_prop) %>% 
  filter(casestudy == "de5") %>%
  select(casestudy, method, prop_yeastsim)

@@

rank.tab$method <- factor(rank.tab$method,
                          levels = yeastsim.tab$method[order(yeastsim.tab$prop_yeastsim)])

ggplot(rank.tab, aes(y = prop_casestudy, x = method, group = method, fill = method)) +
  geom_boxplot() +
  scale_fill_manual(values=col) +
  theme_bw() +
  xlab("Method (ordered by rejections in Yeast simulation (n=5))") + 
  ylab("Proportion of maximum rejections in casestudies")
ggsave(file.path(outdir, "Figure_simVcasestudyRanks.pdf"), width=6, height=4)
```

>>>>

```{r}
library(ggbeeswarm)

casestudy.tab <- mutate(casestudy.tab, prop_casestudy = mean_prop) %>%
  select(casestudy, method, prop_casestudy)
yeastsim.tab <- yeastsim.tab %>% 
  mutate(prop_yeastsim = mean_prop) %>% 
  filter(casestudy == "de5") %>%
  select(casestudy, method, prop_yeastsim)

@@

rank.tab$method <- factor(rank.tab$method,
                          levels = yeastsim.tab$method[order(yeastsim.tab$prop_yeastsim)])
x <- match(rank.tab$casestudy.x, dataset)
rank.tab$casestudy <- casestudy[x]

ggplot(rank.tab , 
       aes(y = prop_casestudy, x = method, group = method, color = Method)) +
  geom_boxplot(aes(x = prop_yeastsim, group = as.factor(prop_yeastsim), y = prop_casestudy),
                   alpha = 0.3, width = 0.04, outlier.shape = NA) +
  geom_quasirandom(aes(x = prop_yeastsim, y = prop_casestudy, color = Method, shape = casestudy),
                   alpha = 0.6, cex=3, width = 0.002,  groupOnX = TRUE,
                   varwidth = TRUE) +
  scale_color_manual(values=col) +
  theme_bw() +
  xlab("Proportion of maximum rejections in yeast simulation (n=5)") +  
  ylab("Proportion of maximum rejections in casestudies") +
  labs(shape = "Case Study") 
ggsave(file.path(outdir, "Figure_simVcasestudyRanks_points.pdf"), width=6, height=4)
